Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2018-01-16 paper-ieee-trans.tex
Added Cris comments

\begin{table}[!h]
%% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Features on software reliability in EC-projects}
\label{tab:feat}
\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
\begin{adjustbox}{max width=0.5\textwidth}
\begin{tabular}{llllllll}
\hline
\hline
Feature & DataGrid & EGEE I, II, III & ETICS 1, 2 & EMI & EGI-Inspire \& Engage & INDIGO-DataCloud\\
\hline
\hline
Architecture Task Force&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Communication Handling&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Requirements Handling&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Agile Methodologies&&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Source code inspection&&&&$\surd$&&$\surd$\\
Build/Testing Management Procedure&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Software Product Metrics&$\surd$&$\surd$&$\surd$&&$\surd$&$\surd$\\
Quality Criteria Definition&&&$\surd$&$\surd$&$\surd$&$\surd$\\
%Manual Certification Procedure&$\surd$&$\surd$&&$\surd$&&\\
Automatic Certification&&&$\surd$&&$\surd$&$\surd$\\
Auto-generated Documentation&&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
DevOps practices adoption (CI, CD)&&&&&&$\surd$\\
\hline
\hline
\end{tabular}
\end{adjustbox}
\end{table}

>>>>

\begin{table}[!h]
%% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Features on software reliability in EC-projects}
\label{tab:feat}
\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
\begin{adjustbox}{max width=0.5\textwidth}
\begin{tabular}{llllllll}
\hline
\hline
Feature & DataGrid & EGEEs & ETICSs & EMI & EGIs & INDIGO-DC\\
\hline
\hline
Architecture Task Force&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Communication Handling&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Requirements Handling&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Agile Methodologies&&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Source code inspection&&&&$\surd$&&$\surd$\\
Build/Testing Management Procedure&$\surd$&$\surd$&$\surd$&$\surd$&&$\surd$\\
Software Product Metrics&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Quality Criteria Definition&&&$\surd$&$\surd$&$\surd$&$\surd$\\
%Manual Certification Procedure&$\surd$&$\surd$&&$\surd$&&\\
Automatic Certification&&&$\surd$&&$\surd$&$\surd$\\
Auto-generated Documentation&&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
DevOps practices adoption (CI, CD)&&&&&&$\surd$\\
\hline
\hline
\end{tabular}
\end{adjustbox}
\end{table}
